Multisensor Architecture for an Intersection Management System

### 2015-04-06 ch3-arch_sys.tex
Some corrections and modifications
Created a draft for the structure of Chapter 3
First paragraph of chapter 3

% Architecture Description and system specifications
% 	* Multisensor IMS
%		
%		* Processing Stages
%		* Fusion approaches
%		* Methods and techniques
%		* Architecture proposal

%	* Validation approaches
%		* Transportation and Traffic Simulations
%			* Simulators Classification
%		* Intersection monitoring Datasets
%			* POSSi Dataset
%			* KoPER Dataset

>>>>

% Architecture Description and system specifications
% 	* Multisensor IMS		
%		* Processing Stages
%		* Fusion approaches
%		* Methods and techniques
%		* Architecture proposal
%	* Validation approaches
%		* Transportation and Traffic Simulations
%			* Simulators Classification
%		* Intersection monitoring Datasets
%			* POSSi Dataset
%			* KoPER Dataset

\chapter {Architecture Description and System Specification}

Although several types of sensors are used for intersection monitoring and supervision, the use of cameras, lasers and lidars has increased due to advances in sensors and computing capabilities. These enhancements have allowed to deploy more of these types of sensors per scenario and is required to define some processing stages from raw data capture through decision and control. Also is needed to test and validate the developments prior to a real and full functional implementation. The first part of this chapter describe main stages in a intersection management system based on image and range sensors, fusion approaches and methods used in these stages and an architeture proposal for the implementation. In the second part, two validation tools for IMS application are compared, simulators and datasets.

\section{Multisensor IMS}
Multicamera and multilasers monitoring systems offer more information about environment that can be merged to provide a better representation of the whole scene, and detect more acurately the objects in the intersection and prevent possible incidents.
\subsection{Processing Stages}
\subsection{Fusion approaches}
\subsection{Methods and techniques}
\subsection{Architecture proposal}
\section{Validation approaches}
\subsection{Transportation and Traffic Simulations}
\subsubsection{Simulators Classification}
\subsection{Intersection monitoring Datasets}
\subsubsection{POSSi Dataset}
\subsubsection{KoPER Dataset}
